---
execute: 
  echo: false
  message: false
  warning: false
  error: false
---
# Happiness and Money

```{r}
#| label: setup

library(readxl)
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
```
```{r}
#| label: dataprep
#| cache: true
#| error: false
#| message: false
#| warning: false

x <- read_excel("data/DataForTable2.1.xls") |>
  drop_na() |>
  mutate(country_name = `Country name`,
         happiness = `Life Ladder`,
         gdp_log = `Log GDP per capita`,
         corruption = `Perceptions of corruption`,
         life_expectancy = `Healthy life expectancy at birth`,
         .keep = "none")
```

```{r}
#| label: graph

x |>
  ggplot(aes(x=gdp_log, y=happiness)) +
    geom_point() +
    labs(title = "Happiness and GDP - All Countries",
         subtitle = "More money seem to relate to greater happiness",
         x = "log(GDP)",
         y = "Predicted happiness",
         caption = "World Happiness Report, 2007-2023") +
    theme_classic()
  
```


## Summary
Does happiness depend on money?  Using data from the World Happiness Report, from 2004 to 2023, we seek to find a relationship between happiness and other socio-economic factors including GDP per capita.  We modeled happiness as a function of GDP, corruption, and life expectancy for all countries represented in the Report.  A country's GDP per capital has a strong positive relationship to the country's happiness.
